Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-18 icmssp-paper/parts/01_introduction.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

\section{Introduction}
Digital image security is a growing concern, and various image encryption schemes have been developed and analyzed in the literature~\cite{murugan_survey_2018, kester_cryptographic_2015, jain_image_2016, singh_image_2015, khoirom_cryptanalysis_2018}. Cryptosystems allow for the secure transmission of data by way of encryption and decryption schemes. 
Of particular interest is homomorphic image encryption, which allows operations to be performed on encrypted images. These operations are then preserved when the images is decrypted. In this manner, images are manipulated without compromising data privacy, as the image being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.

@@

In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}. While secure linear image operations have been implemented~\cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.

@@

To evaluate the performance of homomorphic image manipulation, in Section \ref{sec:chapter_4}, we test the time efficiency and accuracy of common image processing operations under homomorphic encryption. We test for image quality of the resulting images using Mean Squared Error (MSE), Peak Signal to Noise Ratio (PSNR), and Structural Similarity Index (SSIM), which are measures of image quality used for assessing image encryption schemes~\cite{ahmed_benchmark_2016}.

>>>>

\section{Introduction}
Digital image security is a growing concern, and various image encryption schemes have been developed and analyzed in the literature~\cite{murugan_survey_2018, jain_image_2016, khoirom_cryptanalysis_2018}. Cryptosystems allow for the secure transmission of data by way of encryption and decryption schemes. 
Of particular interest is homomorphic image encryption, which allows operations to be performed on encrypted images. These operations are then preserved when the images is decrypted. In this manner, images are manipulated without compromising data privacy, as the image being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.

@@

In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. There is also work on facial recognition on encrypted images~\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}. While secure linear image operations have been implemented~\cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.

@@

To evaluate the performance of homomorphic image manipulation, in Section \ref{sec:chapter_4}, we test the time efficiency and accuracy of common image processing operations under homomorphic encryption. We test for image quality of the resulting images using mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), which are measures of image quality used for assessing image encryption schemes~\cite{ahmed_benchmark_2016}.

### 2019-03-18 icmssp-paper/parts/02_01_cryptosystems.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

Similar to the Paillier cryptosystem, for all $m_1,m_2 \in \mathbb{Z}_u$, the following homomorphic properties hold for the DGK cryptosystem:
\begin{align}
    D(E(m_1)g^{m_2}) &=(m_1+m_2)\bmod u \label{eq:dgk_ctpluspt}\\
    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u \label{eq:dgk_ctplusct}\\
    D(E(m_1)^{m_2}) &= m_1m_2\bmod u. \label{eq:dgk_cttimespt},
\end{align}
which allow for homomorphic operations similar to to that of the Paillier cryptosystem.
As the multiplicative homomorphism (Equation \ref{eq:dgk_cttimespt}) was not presented in the original paper, we provide a short proof here.
\begin{table}[ht]
	\caption{The DGK cryptosystem}
	\label{tab:dgk_summary}
    \begin{tabular}{
        p{\dimexpr 0.2\linewidth-2\tabcolsep}
        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
		\toprule
		Step & Description\\
        \midrule
            Generate \newline Keys &
            Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
            Denote $n = pq$. \newline
            Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
            The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
            \\
            Encrypt &
            The encryption of a plaintext $m \in \mathbb{Z}_u$ given the public key is $E(m) = g^m \cdot h^r \mod{n}$, where $r$ is a random integer in $\mathbb{Z}_n$.
            \\
            Decrypt &
            To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, we compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
            \\
	    \bottomrule
    \end{tabular}
\end{table}

>>>>

Similar to the Paillier cryptosystem, for all $m_1,m_2 \in \mathbb{Z}_u$, the following homomorphic properties hold for the DGK cryptosystem:
\begin{align}
    D(E(m_1)g^{m_2}) &=(m_1+m_2)\bmod u \label{eq:dgk_ctpluspt}\\
    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u \label{eq:dgk_ctplusct}\\
    D(E(m_1)^{m_2}) &= m_1m_2\bmod u, \label{eq:dgk_cttimespt}
\end{align}
which allow for homomorphic operations similar to to that of the Paillier cryptosystem.
As the multiplicative homomorphism (Equation \ref{eq:dgk_cttimespt}) was not presented in the original paper, we provide a short proof here.
\begin{table}[ht]
	\caption{The DGK cryptosystem}
	\label{tab:dgk_summary}
    \begin{tabular}{
        p{\dimexpr 0.2\linewidth-2\tabcolsep}
        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
		\toprule
		Step & Description\\
        \midrule
            Generate \newline Keys &
            Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
            Denote $n = pq$. \newline
            Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
            The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
            \\
            Encrypt &
            The encryption of a plaintext $m \in \mathbb{Z}_u$ given the public key is $E(m) = g^m \cdot h^r \mod{n}$, where $r$ is a random integer in $\mathbb{Z}_n$.
            \\
            Decrypt &
            To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, we compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
            \\
	    \bottomrule
    \end{tabular}
\end{table}

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

To implement non-linear intensity transformations in a privacy--preserving system, it is necessary to evaluate logarithm and exponential functions using closed--form approximations, since the arguments of the functions are unknown. An applicable approximation for the logarithm, found in \cite{pcsc-paper}, is
% TODO: HOW ABOUT BGV
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
	\end{split}
\end{align}
where
\begin{align*}
	\begin{split}
	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
	&- 121239315x - 257804775\\
	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
	&+ 3122577).
	\end{split}
\end{align*}
This approximation can be computed under a homomorphic cryptosystem which supports floating--point operations by precomputing the value of $\log{16}$ in the plaintext domain.
% \begin{align}\label{eq:optimal_log_approximation}
% 	\begin{split}
% 		&\log\left(1+x\right) \\
% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
% 		&+ \log{16}.
% 	\end{split}
% \end{align}

>>>>

To implement non-linear intensity transformations in a privacy--preserving system, it is necessary to evaluate logarithm and exponential functions using closed--form approximations, since the arguments of the functions are unknown. An applicable approximation for the logarithm, found in \cite{pcsc-paper}, is
% TODO: HOW ABOUT BGV
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16} ,
	\end{split}
\end{align}
where
\begin{align*}
	\begin{split}
	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
	&- 121239315x - 257804775\\
	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
	&+ 3122577).
	\end{split}
\end{align*}
This approximation can be computed under a homomorphic cryptosystem which supports floating-point operations by precomputing the value of $\log{16}$ in the plaintext domain.
% \begin{align}\label{eq:optimal_log_approximation}
% 	\begin{split}
% 		&\log\left(1+x\right) \\
% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
% 		&+ \log{16}.
% 	\end{split}
% \end{align}

### 2019-03-18 icmssp-paper/parts/03_methodology.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

\section{Methodology}
\label{sec:chapter_3}
% We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications. In particular, the study consists of the following:
% \begin{itemize}
% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
% \end{itemize}

% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
% Two experiments are conducted in this study:
% \begin{enumerate}
% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
% \end{enumerate}
% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

\subsection{System Implementation}
A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

@@

For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT). The PDT was generated by running the image operation on the original image. The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT. The three images (PT, PDT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.

We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}. In describing each test, we let $R_i$ denote a value in an image $R$, where $1 \leq i \leq N$.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2$ and $c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}

Computation of the MSE between the PDT and CDT, PSNR of the CDT, and SSIM(PDT,CDT) was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.

\subsubsection{Facial Recognition Tests}
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.

>>>>

\section{Methodology}
\label{sec:chapter_3}
\subsection{System Implementation}
A wrapper library was created in Python 3.7.1 that combines the Paillier, DGK, and BGV cryptosystems into a unified interface.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

@@

For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT). The PDT was generated by running the image operation on the original image. The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT. The PT, PDT, and CDT were then compared using image quality benchmarks to evaluate the applicability of each homomorphic encryption scheme.

We perform three tests to ascertain the preservation of image quality after encryption and decryption: mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}. These statistics were computed using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
\begin{description}
	\item [Mean Squared Error (MSE).]
	By computing mean squared error between the PDT and the CDT, we obtain a measure of how much image quality is retained after encryption, transformation, and decryption. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	We compute the PSNR from the MSE. The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	We compute the SSIM between the PDT and the CDT. The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}
\subsubsection{Facial Recognition Tests}
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.
